TODO title

### 2017-01-20 doc/paper/paper.tex
Supplementary analysis and bar-beta

\subsection{Leaky, competing accumulator model}
We implement the widely used, leaky, competing accumulator (LCA) model proposed 
by~\citeA{usher2001}.  The dynamics for the state variables $x_i,\ i < N$, where 
$N$ is the number of choices, are given by
\begin{equation}\label{eqn:usher-mcclelland}
    \begin{split}
        \dif x_i &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) 
        \frac{\dif t}{\tau} \\
    x_i &\rightarrow \max(x_i, 0)
    \end{split}
\end{equation}
where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral 
inhibition, and $\tau$ the time constant. Note that one usually wants to set $k 
= \beta$ because TODO\@. Here, we chose $k = \beta = 1$. TODO what does changing 
this control? Why can we fix it at 1? (Or at least why is it convenient?)

@@

\subsection{Independent accumulator model}
The other investigated winner-take-all mechanism is an independent accumulator 
(IA) model, i.e.~there is no interaction like mutual inhibition among the 
accumulators. Compared to prior similar models (TODO refs), however, we add 
a second layer of independent, non-recurrent populations that get input from the 
first layer in a one to one projection. We decode the shifted Heaviside function 
$\bar{x}_{2,i} = \Theta(x^2_i - \vartheta)$ from it where $\vartheta = 0.8$ is 
a threshold value controlling how much evidence needs to be accumulated to 
produce an output.
The Heaviside decoded output of layer 2 projects back to layer 1 to add 
$\bar{x}_{2,i} - 2\sum_{j \neq i} \bar{x}_{2,j}$ to the input of $x_{1,i}$. As 
effect the choice will be stabilized while all other state variables will be 
suppressed once one of the accumulators reaches the threshold $\vartheta$.  The 
dynamics are described by the following equations.
\begin{equation}
    \begin{split}
        \dif x_{1,i} &= \lambda \rho_i \frac{\dif t}{\tau_1} + \left( 
            \bar{x}_{2,i} - 2\sum_{j \neq i} \bar{x}_{2,j} \right) \frac{\dif 
            t}{\tau_2} \\
    x_{1,i} &\rightarrow \max(x_{1,i}, 0) \text{.}
    \end{split}
\end{equation}

@@

\subsection{Metrics}
To test and compare the two WTA mechanisms we provide an input of $\rho_i 
= u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and 
$\eta_i$ Gaussian white noise with standard deviation $\sigma$. Thus, without 
loss of generality, the first state variable receives the strongest input and 
all other state variables receive input that is smaller by $s$. We chose this 
input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will 
decrease and the effective number of choices to decide between would decrease  
As $s \rightarrow 0$ the problem gets more difficult. We will use $u = 1$ as 
long as not indicated otherwise and set the number of dimension to $d = 10$.  In 
both WTA models we use 200 neurons for each dimensions. In the IA network this 
are split as 150 neurons for each layer 1 population and 50 neurons for each 
layer 2 population. Further parameters are summarized in Table~\ref{tbl:params}.
\begin{table}
    \caption{Summary of parameter values.}\label{tbl:params}
    \begin{tabular}{ll}
        LCA time constant & $\tau = \SI{0.1}{\second}$ \\
        LCA recurrency parameters & $k = \beta = 1$ \\
        IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
        IA feed-back time constant & $\tau_2 = \SI{100}{\second}$ \\
        IA threshold & $\vartheta = 0.8$ \\
        Recurrent synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.1}{\second}$ \\
        Feed-forward synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{5}{\milli\second}$ \\
        Output decoding synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{10}{\milli\second}$
    \end{tabular}
\end{table}

>>>>

\subsection{Leaky, competing accumulator model}
We implement the widely used, leaky, competing accumulator (LCA) model proposed 
by~\citeA{usher2001}.  The dynamics for the state variables $x_i,\ i < N$, where 
$N$ is the number of choices, are given by:
\begin{equation} \label{eqn:usher-mcclelland}
    \begin{split}
        \frac{{\partial x}_i}{\partial t} &= \left(\rho_i - kx_i - \beta \sum_{j \neq i} x_j\right) \frac{1}{\tau} \\
        x_i &\rightarrow \max(x_i, 0) ,
    \end{split}
\end{equation}
where $\rho_i$ is the external input, $k$ is the leak rate, $\beta$ the lateral 
inhibition, and $\tau$ the time constant.
We set $k = \beta = 1$, since this will guarantee that the winning state converges to the value of its input, while the losing states converge to zero.
Other choices of $k$ merely alter the effective $\tau$ and the effective gain on the input, while other choices of $\beta$ will produce unwanted behaviour (see supplementary analysis).

@@

\subsection{Independent accumulator model}
The other investigated winner-take-all mechanism is an independent accumulator 
(IA) model, i.e.~there is no interaction like mutual inhibition among the 
accumulators. Compared to prior similar models (TODO refs), however, we add 
a second layer of independent, non-recurrent populations that get input from the 
first layer in a one to one projection. We decode the shifted Heaviside function 
$\bar{x}_{2,i} = \Theta(x^2_i - \vartheta)$ from it where $\vartheta = 0.8$ is 
a threshold value controlling how much evidence needs to be accumulated to 
produce an output.
The Heaviside decoded output of layer 2 projects back to layer 1 to add 
$\bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j}$ to the input of $x_{1,i}$.
For $\bar{\beta} = 2$ (see supplementary analysis), the correct choice will self-excite while all other state variables will be 
suppressed once one of the accumulators reaches the threshold $\vartheta$.  The 
dynamics are described by the following equations:
\begin{equation}
    \begin{split}
        \frac{{\partial x}_{1,i}}{\partial t} &= \lambda \rho_i \frac{1}{\tau_1} + \left( 
            \bar{x}_{2,i} - \bar{\beta} \sum_{j \neq i} \bar{x}_{2,j} \right) \frac{1}{\tau_2} \\
        x_{1,i} &\rightarrow \max(x_{1,i}, 0) .
    \end{split}
\end{equation}

@@

\subsection{Metrics}
To test and compare the two WTA mechanisms we provide an input of $\rho_i 
= u - s \delta_{1i} + \eta_i$ where $u$ is the strength of the strongest input, 
$s$ the target separation to all other inputs, $\delta$ the Kronecker delta, and 
$\eta_i$ Gaussian white noise with standard deviation $\sigma$. Thus, without 
loss of generality, the first state variable receives the strongest input and 
all other state variables receive input that is smaller by $s$. We chose this 
input as for $\rho_i \rightarrow 0$ the influence of input $\rho_i$ will 
decrease and the effective number of choices to decide between would decrease  
As $s \rightarrow 0$ the problem gets more difficult. We will use $u = 1$ as 
long as not indicated otherwise and set the number of dimension to $d = 10$.  In 
both WTA models we use 200 neurons for each dimensions. In the IA network this 
are split as 150 neurons for each layer 1 population and 50 neurons for each 
layer 2 population. Further parameters are summarized in Table~\ref{tbl:params}.
\begin{table}
    \caption{Summary of parameter values.}\label{tbl:params}
    \begin{tabular}{ll}
        LCA time constant & $\tau = \SI{0.1}{\second}$ \\
        LCA recurrency parameters & $k = \beta = 1$ \\
        IA accumulation time constant & $\tau_1 = \SI{0.1}{\second}$ \\
        IA feed-back time constant & $\tau_2 = \SI{0.1}{\second}$ \\
        IA threshold & $\vartheta = 0.8$ \\
        Recurrent synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.1}{\second}$ \\
        Feed-forward synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.005}{\second}$ \\
        Output decoding synaptic time constant & $\tau_{\mathrm{s}} 
        = \SI{0.01}{\second}$
    \end{tabular}
\end{table}
